Hazelnut: A Bidirectionally Typed \\ Structure Editor Calculus

### 2016-07-07 agda.tex
clarified missing thms

This development is available in the supplemental material. At the time of submission, the full set of rules is available and the proofs of Theorem \ref{thrm:actsafe}, Theorem \ref{lemma:movement-erasure} and a number of technical lemmas that we elided or mentioned informally in the text are complete. We also have nearly all of the cases of Reachability and Constructability complete (and see no major barrier to the remaining cases -- they are simply tedious.) \todo{include link to repos in non-anonymous supplementals}\todo{talk about determinism either here or there}

>>>>

This development is available in the supplemental material. At the time of submission, the full set of rules is available and the proofs of Theorem \ref{thrm:actsafe}, Theorem \ref{lemma:movement-erasure} and a number of technical lemmas that we elided or mentioned informally in the text are complete. We also have nearly all of the cases of Reachability and Constructability complete, and we see no major barrier to the remaining cases -- we prioritized developing a clear exposition of our contributions after proving representative cases and finding that they were straightforward. The remaining cases will be completed in the repository linked in the non-anonymous supplementary material.\todo{include link to repos in non-anonymous supplementals}\todo{talk about determinism either here or there}

### 2016-07-07 implementation.tex
clarified missing thms

>>>>

The programmer examines a view generated from each edit state and produces actions in some implementation-defined manner (e.g. using a keyboard, mouse, touchscreen, voice interface, or neural implant.) Each new action causes a new abstract edit state to arise according to an implementation of the action semantics. This then causes a new to arise. This is a simple event-based functional reactive programming model \cite{Wan:2000:FRP:349299.349331}.

If an action is not well-defined according to the action semantics, the implementation must reject it. In fact, an implementation is encouraged to present an ``action palette'' that either hides or visibly disables actions that are not well-defined (see below.)
